---
title: "bjjanalyse"
author: "Zhengzhi Lin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#### Motivation
I am always a big fan of jiu-jitsu,a special martial art. Nowadays, jiu-jitsu is still at its beginning of spreading in China. Still very few people know it , let alone train it. Everything is like chaos, because jiu-jitsu just grows agressively, I have a strong feeling it will furish in China as well as Tae koon doo, another martial art travelled from Korea. Therefore, I think it is a good time to collect some data and record this time. I need to know these people's age, gender,etc. Information about what kind of people they are, how many times they train a week.....
And I have a sense that in China, jiu-jitsu is kind of exclusive to certain groups of people, who have high salary, are young and not busy working, love martial arts, be willing to train for a long time. I hope I can prove my guess  through my package and my data, though they are not complete yet.

#### The data I collect
I collect the data of jiu-jitsu trainers. It includes their age(under 18,18 to 25  etc), gender, how long they've been training(1 year or 1.5 year), their money spent on jiu-jitsu(for example 8000 Chinese yuan per year), and their training frequency(for instance, 1 to 3 times a week or 3 to 5 times a week),
competition plan(for example, 1 times a year).

#### Where I get the data?
I use a popular China websit to create a survey form and send it to as many jiu-jitsu groups as I can.

#### Survey link：https://www.wjx.cn/jq/16656266.aspx

#### What is this package for?
This packge is created for plotting information in the jiu-jitsu data, and doing some caculations with the data. It deals with a lot variables in the data collected by the survey.

By using this package, we can easily get data from googlesheets through a single function. We can also use simplified function building some dataframe and analyse special parts of data, rather than using repetitions or create functions temporarily.

We can also use one function to caculate the mean of money spend per year. Getting injure rate of this sport.

As time move on, I will keeping adding new abilities for this package.

#### First, we should ask googlesheets permission code.
```{r,message=FALSE}
library(BjjAnalyse)
authoriz()
```

#### Examples: Get collection of data from googlesheets, and put it in object dat.

```{r,message=FALSE}
library(knitr)
dat <- read_data()
kable(dat[1:10,1:10])
```

#### Example: plot a hist graph about age and trainning frequency by using age_freq().

```{r}
library(BjjAnalyse)
age_freq(dat)
```

#### Example: People might want to know the injure rate of this kind of sport.We can use inj_rate()

```{r}
inj_rate(dat)

```

#### Example: If I want to know the average amount money of each location,I can use loc_mean() function.

```{r}
library(BjjAnalyse)
loc_mean(dat)[1:5]
```

#### Example: Get a pie graph of the percentage of each belt rank of self rank in all, in the example we can see for instance, people who is white belt is 69.51% of all.

```{r}
library(BjjAnalyse)
self_rank(dat)

```
